---
title: 'Week3: Plotly Presentation'
author: "Boris Blazej"
date: '2022-03-28'
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(readr)
library(tidyverse)
library(plotly)
```

## Covid-19 vaccination figures from Austria

The following charts show some Covid-19 vaccination figures from my home country: Austria.

The Data is derived from [Open Data Austria](https://www.data.gv.ah), a governmental open data platform. 
It represents the status as of 2022-03-27 21:59:59.

The source code for this analysis can be downloaded from [Github](https://github.com/borisblazej/w3_proj_plotly).



## The Data

```{r data, warning=FALSE}

data_url <- "https://info.gesundheitsministerium.gv.at/data/COVID19_vaccination_doses_agegroups.csv"

download.file(data_url, "./data/at_vaccination.csv")

at_vaccination <- read_delim(
    "data/at_vaccination.csv",
    delim = ";",
    escape_double = FALSE,
    col_types = cols(
        date = col_skip(),
        state_id = col_skip()
    ),
    trim_ws = TRUE
)

head(at_vaccination)


```

## Most-applied Vaccine

BioNTechPfizer is by far the most-applied vaccine so far in Austria.

```{r vaccine, echo = FALSE}

tot_vacc <- at_vaccination %>%
    group_by(vaccine) %>% 
    summarise(doses = sum(doses_administered_cumulative), 
              .groups = "drop") %>% 
    arrange(desc(doses))
    
g <- ggplot(tot_vacc, aes(x = vaccine, y = doses, fill = vaccine)) +
    geom_col()

ggplotly(g)

```

## Difference in Age Groups

Interestingly, the vaccines do not distribute identically across age groups. Whereas AstraZeneca and BioNTechPfizer peak at 55-64 (= the overall distribution peak), Janssen peaks at 25-34 and Moderna peaks at 45-54 years.

```{r age_groups}
at_vaccination_enr <- at_vaccination %>%
    left_join(tot_vacc, by = "vaccine") %>%
    mutate(share = doses_administered_cumulative / doses)

age_vac_share <- at_vaccination_enr %>%
    group_by(vaccine, age_group) %>%
    summarise(vacc_share = sum(share), .groups = "drop")

g2 <- ggplot(age_vac_share, aes(
    x = 1,
    y = 1,
    color = vaccine,
    size = vacc_share
)) +
    geom_point() +
    geom_text(aes(label = round(vacc_share, 2)), 
            colour = "black", 
            size = 2) +
    facet_grid(age_group ~ vaccine) +
    scale_x_discrete(position = "top") +
    scale_y_discrete(position = "left") +
    labs(x = NULL, y = NULL) +
    theme(
        legend.position = "none",
        panel.background = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_blank()
    )

ggplotly(g2)

```

## Controll: Overall Age Structure

```{r age_control, echo = FALSE}

age_vacc <- at_vaccination %>%
    group_by(age_group) %>% 
    summarise(doses = sum(doses_administered_cumulative), 
              .groups = "drop") %>% 
    arrange(desc(doses))
    
g2 <- ggplot(age_vacc, aes(x = age_group, y = doses)) +
    geom_col()

ggplotly(g2)

```
